---
title: "Cryptography Course Target Audience.(EDA)"
author: "Gathoni Njoroge"
date: '2022-05-26'
output: pdf_document
---
# Exploratory Data Analysis of an online Cryptography Course Advert.
## 1) Defining the question.
### a) Specifying the question.
#### Who is the most likely target audience for an online cryptography course?
### b) The metric of success.
#### Finding a specific group of people who are likely to click on the advertisments given the data available.
### c) The context.
#### Determining which factors make a person one of the target audiences for future forecasting.
### d) Experimental design.
#### i) Loading and reading the data
#### ii) Data cleaning.
#### iii) Exploratory analysis.
#### iv) Conclusion.
#### v) Recommendation.
### e) Appropriateness of the Data Available.
#### The data available has been collected from previous targeted adverts by the same enterpreneur and is therefore apprpriate for this study.
## 2) Loading and reading the data.
```{r}
# loading libraries
#
library(data.table)
library(tibble)
library(tidyverse)
library(corrplot)
library(ggplot2)
library(GGally)


# loading the dataset.
#
target <- fread('http://bit.ly/IPAdvertisingData')

# checking the top of the dataset.
#
head(target)
# checking the bottom of the dataset
#
tail(target)
# Converting dataset into tibble
#
target1 <- tibble(target)
target1
```
## 3) Data cleaning.
```{r}
# checking for missing values
#
colSums(is.na(target1))

# The dataset contains no missing values
```

```{r}
# checking for duplicates
#
duplicates <- target1[duplicated(target1),]
duplicates

# handling duplicates
#
# The dataset contains no duplicated rows
```

```{r}
# checking for and removing outliers using IQR
#

Q1 = quantile(target1$'Age')
Q3 = quantile(target1$'Age')
IQR = IQR(target1$'Age')
no_out = subset(target1, target1$'Age'> (Q1 - 1.5*IQR) & target1$'Age'< (Q3 + 1.5*IQR))
no_out
```

```{r}
# selecting rows where clicked on ad is 1
#
target2 <- no_out %>% filter(no_out$'Clicked on Ad' == 1)
target2
```

```{r}
# dropping redundant variables
#
drop <- c("Timestamp", "Ad Topic Line")
target_ad = target2[,!(names(target2) %in% drop)]
target_ad
```
## 4) Exploratory Analysis.
### Univariate Analysis.
#### Measures of Central Tendency.
```{r}
#calculating mean
#
mean(target_ad$'Daily Time Spent on Site')
mean(target_ad$'Age')
mean(target_ad$'Area Income')
mean(target_ad$'Daily Internet Usage')
```
```{r}
#Calculating median
#
median(target_ad$'Daily Time Spent on Site')
median(target_ad$'Age')
median(target_ad$'Area Income')
median(target_ad$'Daily Internet Usage')
```
```{r}
# Calculating mode
#
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
getmode(target_ad$'Daily Time Spent on Site')
getmode(target_ad$'Age')
getmode(target_ad$'Area Income')
getmode(target_ad$'Daily Internet Usage')
getmode(target_ad$'Male')
```
#### Measures of Dispersion.
```{r}
# calculating minimum values
#
min(target_ad$'Daily Time Spent on Site')
min(target_ad$'Age')
min(target_ad$'Area Income')
min(target_ad$'Daily Internet Usage')
'--------------'
#calculating maximum values
#
max(target_ad$'Daily Time Spent on Site')
max(target_ad$'Age')
max(target_ad$'Area Income')
max(target_ad$'Daily Internet Usage')

```
```{r}
# Get range, 1st and 3rd quantiles
# 
quantile(target_ad$'Daily Time Spent on Site')
quantile(target_ad$'Age')
quantile(target_ad$'Area Income')
quantile(target_ad$'Daily Internet Usage')
```
```{r}
# variance and standard deviation
#
var(target_ad$'Daily Time Spent on Site')
var(target_ad$'Age')
var(target_ad$'Area Income')
var(target_ad$'Daily Internet Usage')
'------------'
sd(target_ad$'Daily Time Spent on Site')
sd(target_ad$'Age')
sd(target_ad$'Area Income')
sd(target_ad$'Daily Internet Usage')
```
```{r}
# frequency of categorical variables
#
library(plyr)
library(dplyr)
country_freq = count(target_ad,  'Country')
country_freq
sorted_by_freq <- country_freq[order(-country_freq$freq),]
sorted_by_freq
```

#### Visualization.
```{r}
#summary of above using boxplots
#
boxplot(target_ad$'Daily Time Spent on Site')
boxplot(target_ad$'Age')
boxplot(target_ad$'Area Income')
boxplot(target_ad$'Daily Internet Usage')
```

```{r}
# visualisation of numeric variables using a histogam
#
hist(target_ad$'Daily Time Spent on Site')
hist(target_ad$'Age')
hist(target_ad$'Area Income')
hist(target_ad$'Daily Internet Usage')
hist(target_ad$'Male')
```

```{r}
# Barplot of countries.
#

x <- table(country_freq$freq)
barplot(x[order(x, decreasing=TRUE)])

```
### Bivariate Analysis
#### Covariance and Correlation.
```{r}
# Covariance of numeric variables
#
drop <- c("Country", "City", "Location", "Ad Topic Line", "Clicked on Ad")
target4 = target_ad[,!(names(target_ad) %in% drop)]
target4

cov(target4)
```
```{r}
#correlation matrix
#
correlation = cor(target4)
correlation
```
#### Visualization.
```{r}
# With a scatterplot matrix
#

plot(target4)
```

```{r}
# visualization of the correlation matrix
#
corrplot(correlation)

```


## 5) Conclusion
#### Give the results of this analysis the most likely group of people to click on the targeted ads are:
#### a)Those aged between 35-45
#### b) Who spend between 50 minutes to an hour per day on the site
#### c) From South Africa, Turkey, Australia. though not limited to this countries only. 
## 6) Recommendation.
#### More data is needed for further analysis. However, what is currently analyzed could still be useful to launch a pilot advertising program and gauge how well it works and reaches the target audience.

